% Chapter Template

\chapter{MS1 meeting report} % Main chapter title

\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{\emph{MS1 meeting report}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Introduction}

This document is a short report about the MS1 meeting. The meeting took place on the 1.10.2014.

\section{Version}


\begin{tabular}{| p{1.5cm} | p{2cm} | p{9cm} | p{1.5cm} |}
    \hline
    Version & Date      & Change & Author \\ \hline
    1.0    & 1.10.2014        & Setup document / text                                        & JR \\ \hline
\end{tabular}


\section{Attendees}
\begin{itemize}
\item Joel Rolli
\item Michael Kaufmann
\item Patrick Huber
\item Patrik Lengacher
\end{itemize}

\section{Delivery objects}

\begin{itemize}
\item System specification
\item Sketch software architecture
\item Short presentation CI environment
\item Draft risk evaluation
\end{itemize}

\section{Decisions}

The risk evaluation and the CI environment are approved. 
The evaluation of the text extraction was discussed again and it was decided that the evaluation is still done with Words instead of HTML blocks. Doing the evaluation with HTML blocks can still be done but is not part of the PAWI project and would be bonus content. 
Furthermore it was decided that no handmade test data is needed and the data from cleanEval and Gold standard are used for this project.
The draft of the software architecture is ok but needs to be digitalized.
The software architecture needs to be extended with additional data about the analysis of the extracted data. Which means all the formulas for TN, FP, TP, FN etc. needs to be defined.


\section{Rework}

Following rework needs to be don until the 5.10.2014

\begin{itemize}
\item Extendes software specification
\item Digital version of software architecture sketch
\end{itemize}




